---
title: "GEO-511 Semester Project"
author: Austin Izzo
subtitle: A look into community solar projects across the US. 
---

# Introduction
With the expansion of solar energy throughout the United States in the past year, community solar projects have become increasingly popular. Community solar projects often consist of a partnership between the public, government entities and the business sector to install solar energy throughout a community. The outcomes of such programs can be prosperous for all entities involved. Although a seemingly common sense solution to part of the nation's energy challenge, community solar projects are a relatively new concept and spatial trends in where these projects are taking place. 

Research Question: In this analysis, the goal will be to identify what role the political climate (state and county level), and public perception of global warming will have in installment of community solar projects. 


# Materials and methods

1. Extract all data into R creating separate tables for each. 
2. Convert source 1 into a tibble 
3. Join source 1 and source 3 by county 
4. Identify what county each solar project is in and create column in source 2 table for this. 
5. Create two maps on with the counties either red or blue or political affiliation and the other displaying a color gradient (fill in ggplot) to display the public perception for each county. 
7. Now the solar projects will be mapped to each maps. 
8. Sections will be created in the report for the impact of either public perception or political       affiliation. 
9. Within each section the visuals that will be included will be: 
  1. Scatter Plot of variable vs solar projects
  2. Scatter Plot of variable vs size of system
  3. Summary Tables for each variable 


Load any required packages in a code chunk (you may need to install some packages):

```{r, message=F, warning=F}
#Load neccessary Libraries
library(dbplyr)
library(jsonlite)
#install.packages("xml2")
library(xml2)
library(readr)
#install.packages("readxl")
library(readxl)
library(sf)
library(ggplot2)
library(sf)
library(tidyverse)
#install.packages("spData")
library(spData)
#install.packages("maps")
library(maps)
library(formattable)
```

## Download and clean all required data
```{r}
#Get that Data 
#DSIRE_url <- "http://programs.dsireusa.org/api/v1/getprograms/json"
#DSIRE_data <- fromJSON(DSIRE_url)

#DSIRE_url_xml <- "http://programs.dsireusa.org/api/v1/getprograms/xml"
#DSIRE_data2 <- read_html(DSIRE_url_xml)

#Load in all of the DSIRE datasets
DSIRE_program <- read_csv("program.csv")
DSIRE_parameter_set <- read_csv("parameter_set.csv")
DSIRE_parameter <- read_csv("parameter.csv")
DSIRE_state <- read_csv("state.csv")
names(DSIRE_state)<- c("state_id", "abbreviation", "name", "is_territory")
DSIRE_program_tech <- read_csv("program_technology.csv")
DSIRE_technology <- read_csv("technology.csv")
DSIRE_technology_category <- read_csv("technology_category.csv")

#join the DSIRE datasets by their relevant keys creating one "Final" table with relevant information
DSIRE_program2 <- inner_join(DSIRE_program,DSIRE_state, by = "state_id")
DSIRE_program3 <- inner_join(DSIRE_program2, DSIRE_parameter_set, by = c("id" = "program_id"))
DSIRE_program4 <- inner_join(DSIRE_program3,DSIRE_parameter, by = c("id" = "parameter_set_id"))
DSIRE_program5 <- inner_join(DSIRE_program4,DSIRE_program_tech, by = c("id" = "program_id"))
DSIRE_program6 <- inner_join(DSIRE_program5, DSIRE_technology, by = c("technology_id" = "id"))
DSIRE_program_final <- inner_join(DSIRE_program6, DSIRE_technology_category, by = c("technology_id" = "id"))


NREL_url <- "https://data.nrel.gov/files/114/NREL_Community_Solar_Project_List_6_28_2019%20FINAL.xlsx"
NREL_path <- "NREL_Community_Solar_Project_List_6_28_2019FINAL.xlsx"
NREL_Data <- read_xlsx(NREL_path, sheet = 2)
names(NREL_Data) <- c("Project", "City", "State", "Utility", "Size(kWh)","Year","Latitude", "Longitude")

Harvard_url <- "https://dataverse.harvard.edu/api/access/datafile/:persistentId?persistentId=doi:10.7910/DVN/VOQCHQ/FQ9NBF"
Harvard_Data <- read_tsv(Harvard_url)

state_geom<- map_data("state")
```
Count the number of solar incentives per state
```{r}
#Count the number of solar incentives per state
DSIRE_program_table <- DSIRE_program_final%>%
  filter(is_entire_state == 1)%>%
  filter(name.x.x == "Solar Photovoltaics")
incentives_total_state <- stats::aggregate(DSIRE_program_table$is_entire_state, by =list(state_id = DSIRE_program_table$state_id), FUN = sum )

#join to find state name 
DSIRE_program_table2 <- inner_join(incentives_total_state, DSIRE_state,  by = c("state_id" = "state_id"))%>%
  filter(is_territory == 0)
DSIRE_program_table2$name <- tolower(DSIRE_program_table2$name)

#add state geometry
DSIRE_program_table3 <- full_join(DSIRE_program_table2, state_geom, by = c("name" = "region"))
```





Create spatial distribution plot: 
```{r}
plot1 <- ggplot()+
  geom_polygon(data = DSIRE_program_table3, aes(x = long, y = lat, group = group, col = "blue", fill= as.numeric(x)))+
  coord_fixed(1.5)+
  geom_point(NREL_Data, mapping = aes(x = Longitude , y = Latitude, col = "red", alpha = .8))+
  theme_void()
```

Create Aggregation tables of solar installations
```{r}
kwh_total_state <- stats::aggregate(NREL_Data$`Size(kWh)`, by =list(State=NREL_Data$State), FUN = sum )
kwh_mean_state <- stats::aggregate(NREL_Data$`Size(kWh)`, by =list(State=NREL_Data$State), FUN = mean )
```

# Results

Spatial Distibution of Community Solar Installations - Provided by NREL
```{r, fig.width=8, fig.height=4, fig.cap="Map of completely random data", echo = FALSE, warning = FALSE}
plot1
```

Show the total amount of power generated per state (kWh)
```{r, fig.width=8, fig.height=4, fig.cap="Map of completely random data", echo = FALSE, warning = FALSE}
formattable(kwh_total_state)
```

Show the mean size of community solar installations (kWh)
```{r, fig.width=8, fig.height=4, fig.cap="Map of completely random data", echo = FALSE, warning = FALSE}
formattable(kwh_mean_state)
```

# Conclusions

What have you learned?  Are there any broader implications?

# References/Data Sources

Source 1: Yale Climate Opinion Maps 2018  
  <pre>
  Source: https://climatecommunication.yale.edu/visualizations-data/ycom-us-2018/?est=happening&type=value&geo=county  
  Type: CSV  
  Data to be used: State, County, global warming happening?  
  Purpose: Identify the public perception of global warming at a county level  
   </pre>
  
Source 2: NREL Community Solar Projects  
  <pre>
  Source: https://data.nrel.gov/submissions/114  
  Type: CSV  
  Data to be used: Project name, lattitude, longitude, system size, year of interconnection  
  Purpose: To identify where community solar projects happening 
  </pre>
  
Source 3: MIT Election Lab County Political Affiliation  
  <pre>
  Source: https://dataverse.harvard.edu/file.xhtml?persistentId=doi:10.7910/DVN/VOQCHQ/FQ9NBF  
  Type: CSV  
  Data to be used: County, Party, Year  
  Purpose: To identify political affiliation of counties  
  </pre>




